# Video Game Sales Analysis in R

Going to use R, mostly dpylr and tidyverse libraries to analyze video game sales data set and check original hypothesis'

```{r}

vg_sales <- read_csv('vgsales.csv')
```

Query #1: Finding top selling publishers

```{r}
top_selling_publishers <- vg_sales %>%
    group_by(Publisher) %>%
    summarise(sum(NA_Sales), sum(EU_Sales), sum(JP_Sales), sum(Other_Sales), 'Total_Sales' = sum(Global_Sales)) %>%
    arrange(desc(Total_Sales), .by_group = TRUE)

View(top_selling_publishers)


```

Query #2: Finding top selling platforms

```{r}
top_selling_platforms <- vg_sales %>%
    group_by(Platform) %>%
    summarise(sum(NA_Sales), sum(EU_Sales), sum(JP_Sales), sum(Other_Sales), 'Total_Sales' = sum(Global_Sales)) %>%
    arrange(desc(Total_Sales), .by_group = TRUE)

View(top_selling_platforms)
```

Query #3: Finding top selling genres

```{r}
top_selling_genres <- vg_sales %>%
    group_by(Genre) %>%
    summarise(sum(NA_Sales), sum(EU_Sales), sum(JP_Sales), sum(Other_Sales), Total_Sales = sum(Global_Sales)) %>%
    arrange(desc(Total_Sales), .by_group = TRUE)

View(top_selling_genres)
```

Query #4: Finding top selling years, as well as a look at industry growth over twenty years

```{r}
industry_growth <- filter(vg_sales, (Year == 2015.0) | (Year == 1995.0)) %>%
    group_by(Year) %>%
    summarise(sum(NA_Sales), sum(EU_Sales), sum(JP_Sales), sum(Other_Sales), Total_Sales = sum(Global_Sales)) %>%
    arrange(desc(Total_Sales), .by_group = TRUE)
    


top_selling_years <- vg_sales %>%
    group_by(Year) %>%
    summarise(sum(NA_Sales), sum(EU_Sales), sum(JP_Sales), sum(Other_Sales), Total_Sales = sum(Global_Sales)) %>%
    arrange(desc(Total_Sales), .by_group = TRUE)



#View(top_selling_years)
View(industry_growth)
# ^ you could plug in any two years in industry growth variable to change snapshot view
```

Query #5: Finding with region is responsible for most selling most video games

```{r}
top_selling_regions <- vg_sales %>%
    summarise('North_America' = sum(NA_Sales), 'Europe' = sum(EU_Sales), 'Japan' = sum(JP_Sales), 'Other' = sum(Other_Sales))

View(top_selling_regions)
```

Query #6: Finding top 5 franchises for different popular platforms

You can run each code block below as many times as you want using different title variation in the grepl() pattern argument to see the different games in a franchise series and then lifetime global sales of that franchise is given as an output as well

Top Nintendo:

```{r}
nintendo_top_games <- filter(vg_sales, Publisher == 'Nintendo')
nintendo_franchise_catalog <- filter(vg_sales, grepl('Mario Kart', Name) & (Publisher == 'Nintendo'))


View(nintendo_top_games)
#View(nintendo_franchise_catalog)
#sum(nintendo_franchise_catalog$Global_Sales)
```

Top Playstation:

```{r}
playstation_top_games <- filter(vg_sales, substr(Platform, 1, 2) == 'PS')
playstation_franchise_catalog <- filter(vg_sales, grepl('Spyro', Name) & substr(Platform, 1, 2) == 'PS')

#View(playstation_top_games)
View(playstation_franchise_catalog)
sum(playstation_franchise_catalog$Global_Sales)
```

Top Xbox:

```{r}
xbox_top_games <- filter(vg_sales, substr(Platform, 1, 1) == 'X')
xbox_franchise_catalog <- filter(vg_sales, grepl('Halo', Name) & substr(Platform, 1, 1) == 'X')

#View(xbox_top_games)
View(xbox_franchise_catalog)
sum(xbox_franchise_catalog$Global_Sales)
```

Top PC:

```{r}
pc_top_games <- filter(vg_sales, Platform == 'PC')
pc_franchise_catalog <- filter(vg_sales, grepl('The Sims', Name) & Platform == 'PC')

#View(pc_top_games)
View(pc_franchise_catalog)
sum(pc_franchise_catalog$Global_Sales)


```
